SCM plan for a troubling company

### 2012-01-11 article.tex
added subsection "the change process"

The main idea behind configuration control is to achieve control of changes, what impact they'll have and their costs.

Since this company is relatively small, the extent of CCB and it's usage will be somewhat limited in contrary to the general idea of a CCB.
The CCB consist of the normal lineup with: chairperson, secretary, members and specialists \cite{daniels}. We will select the project manager
to be the chairman and the secretary will be the configuration manager in the company. The project manager will appoint appropriate people to be
members of the CCB and specialists will be contacted on a ``when needed''-basis. There will likely be one representative from each module with the exception
that some modules representatives will be considered experts instead, so that they will not be needed for each meeting.

>>>>

\subsection{The change process}
The main idea behind configuration control is to achieve control of changes, what impact they'll have and their costs.

Since this company is relatively small, the extent of the CCB and it's usage will be somewhat limited in contrary to the general idea of a CCB.
The CCB consist of the normal lineup with: chairperson, secretary, members and specialists \cite{daniels}. We will select the project manager
to be the chairman and the secretary will be the configuration manager in the company. The project manager will appoint appropriate people to be
members of the CCB and specialists will be contacted on a ``when needed''-basis. There will likely be one representative from each module with the exception
that some modules representatives will be considered experts instead, so that they will not be needed for each meeting.
